Unbiased pangenome graphs

### 2022-02-06 manuscript/main.tex
update table
update table with a more compressed hpylori graph
updated statistics and manuscript with hprc+ results using 95% as identity threshold
ambig

Building a graph from an all-to-all alignment does not guarantee that the local structure of the graph is easy to understand.
The all-to-all alignment is not coordinated, with each mapping aligned in isolation, and in consequence it fails to resolve the indel alignment normalization problem \citep{Mose_2019}.
This ambiguity can introduce deeply looping structures in the graph which collapse e.g. microsatellites and other short VNTRs into very small numbers of nodes with very complex local topologies.
Such motifs can cause problems with downstream analysis.
We find that ambiguity about the arrangement of very short matches tends to drive complex local structures in the graph.

>>>>

Building a graph from an all-to-all alignment does not guarantee that the local structure of the graph is easy to understand.
The all-to-all alignment is not coordinated, with each mapping aligned in isolation, and in consequence it fails to resolve the indel alignment normalization problem \citep{Mose_2019}.
This ambiguity can introduce deeply looping structures in the graph which collapse polymorphic microsatellites and other short VNTRs into very small numbers of nodes with very complex local topologies.
Such motifs can cause problems with downstream analysis.
We find that ambiguity about the arrangement of very short matches tends to drive complex local structures in the graph.
